\documentclass[11pt]{article}

\usepackage[margin=0.5in]{geometry}

\begin{document}

    \centerline{\textbf{\huge Mitren Chinoy}}
    \centerline{\large mitren@gmail.com :: 979-777-7513 :: @nertim}
    \centerline{\large https://github.com/nertim :: https://linkedin.com/in/mitren :: https://twitter.com/nertim}


    \section*{Introduction}

        Full stack software developer with experience throughout the entire software life cycle from design to maintenance. Passionate about learning/teaching new concepts and mentoring junior devs. I am interested in pursing a career allowing me to guide a team of individuals to solve interesting technical challenges.

    \section*{Programming languages}
    Listed in the order of proficiency
        \begin{itemize}
            \item C\#
            \item Javascript (familiarity with Angular and React)
            \item HTML
            \item Python (mostly for fun/personal projects)
            \item CSS
        \end{itemize}

    \section*{Experience}

        \subsection*{2013 - Present: Microsoft}
            Senior Software Engineer
            \begin{itemize}
                \item Products worked on: Azure Monitoring (autoscale), Azure LogicApps, Azure WebApps, Azure FunctionApps
                \item Architect and developed experiences for the Azure Portal. Two of the largest ones are for WebApp creates and deployments.
                \item Worked with PMs, Customers, and Designers to re-design existing scenarios and design brand new scenarios. 
                \item Worked on several data pipelines and automated reports. These reports provide targeted information to each team identifying issues in their layers. 
                \item Actively engaged in the code review process to ensure consistency and optimal code.
                \item Maintained documentation and encouraged the team to help maintain.
                \item Mentored junior devs and interns.
            \end{itemize}

        \subsection*{2012 - 2013: Prognosis}
            Lead Software Developer
            \begin{itemize}
                \item Developed and maintained enterprise (Clinical and Financial solutions) EMR application for Hospitals and Clinics.
                \item Created a REST API generator based on the MS SQL database schemas.
                \item Ensured requirements for Meaning Use Stage 2 are researched and developed to meet 2014 deadline.
                \item Ensured requirements for Meaning Use Stage 1 by the Government are met allowing hospitals to attest in a timely manner.
            \end{itemize}

        \subsection*{2008 - 2012: Harris County District Attorney}
            Senior Software Engineer
            \begin{itemize}
                \item Designed, developed, tested, and maintained conversion of legacy web sites, applications, and paper based systems to Rich Internet Applications using .NET technologies (C\#, ASP .NET, MSSQL/T-SQL, and SSRS). Certain applications such as timesheet management and case explorer save 100s of man hours of work and increased productivity.
                \item Accumulated data from various case management databases, using SQL, to provide case activity related statistics including ADA assignments, statuses, physical file movements, and financials.
                \item Designed and developed Web Services and API modules to improve communication with in-house apps and third party software. Generated SQL views which assist in data sharing among inter-county agencies.
                \item Utilized PHP scripts, Visual Studio Macros, and SQL Stored Procedures to eliminate code redundancy.
                \item Developed software engineering documents (class diagrams, actor diagrams, sequence diagrams, and database schema diagrams) for all the applications developed.
                \item Engaged in vendor meetings to evaluate risks and costs involved in third party software implementations.
                \item Provided cost of in-house development (lines of code, development hours, etc) and maintenance versus OTS (Off The Shelf) products.
            \end{itemize}

        \subsection*{2005 - 2008: Ultra Electronics} 
            Software Engineer
            \begin{itemize}
                \item Utilized Object Oriented Analysis and Design, to design and develop a real-time forwarder/receiver module according to the specifications and requirements mentioned in military standards.
                \item Coded the forwarder/receiver module using C++ on Linux platform.
                \item Developed a MySQL database to store data ranges for the fields used from the military standards. This was used for validating the inputs and outputs of forwarder/receiver module.
                \item Developed PHP scripts to extract data from the database and format it in either CSV or XML format. This was used in the documentation for the module.
                \item Participated in Software Engineering documentation (Interface Detail Design, Software Architecture Design, Software Detail Design, and Software Programmers Guide).
                \item Participated in testing process by performing unit and system level testing of application.
                \item Assisted and mentored peers in providing development support and brainstorming throughout various components of the module.
            \end{itemize}

    \section*{Education}

        Bachelors of Science in Computer Engineering, 2005, Texas A\&M University, College Station, TX

    \section*{Hobbies}
        \begin{itemize}
            \item Bicycling
            \item Hiking
            \item Listening to audiobooks
            \item Cooking
        \end{itemize}

\end{document}